---
title: "vignette-bis557"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette-bis557}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bis557)
```

## Package summary

This package includes one dataset `lm_patho`, and two functions `linear_model()` and `lm_grad_descent()`. The purpose of these two functions are solving linear regression problem with different methods.

## data lm_patho
`lm_patho` is a dataset with one dependent variabl, and two correlated independent variables.
```{r}
data("lm_patho")
lm_patho
```

## linear_model() function

The estimated coefficients are calculated in linear algebra way:

$\hat{\beta} = (X^TX)^{-1}X^TY$


## lm_grad_descent() function
The estimated coefficients are obtained by iterating optimization algorithm, and the precision can be regulated by the algorithm finishing criteria. 

## Perform linear regression with lm() function
```{r}
fit_lm <- lm(Sepal.Length  ~ ., iris)
fit_lm$coefficients
```

## Perform linear regression with linear_model() function

```{r}
fit_linear_model <- bis557:::linear_model(Sepal.Length ~ ., iris)
fit_linear_model$coefficients
```

## Perform linear regression with lm_grad_descent() function
```{r}
library(bis557)
fit_gd <- lm_grad_descent(Sepal.Length ~ ., iris)
fit_gd$coefficients
```

## Perform linear regression with lm() function with colinearity problem
```{r}
fit_lm <- lm(y  ~ ., lm_patho)
fit_lm$coefficients
```

## Perform linear regression with linear_model() function with colinearity problem

```{r}
library(bis557)
fit_linear_model <- linear_model(y  ~ ., lm_patho)
fit_linear_model$coefficients
```

## Perform linear regression with lm_grad_descent() function with colinearity problem
```{r}
library(bis557)
fit_gd <- lm_grad_descent(y  ~ ., lm_patho)
fit_gd$coefficients
```


