---
title: "An Example of Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Example of Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r }
library(bis557)
data(iris)
data(lm_patho)

```

## Perform linear regression with lm() function
```{r}
fit_lm <- lm(Sepal.Length  ~ ., iris)
fit_lm$coefficients
```

## Perform linear regression with linear_model() function

```{r}
fit_linear_model <- linear_model(Sepal.Length ~ ., iris)
fit_linear_model$coefficients
```

## Perform linear regression with lm_grad_descent() function
```{r}
fit_gd <- lm_grad_descent(Sepal.Length ~ ., iris)
fit_gd$coefficients
```

## Perform linear regression with lm() function with colinearity problem
```{r}
fit_lm <- lm(y  ~ ., lm_patho)
fit_lm$coefficients
```

## Perform linear regression with linear_model() function with colinearity problem

```{r}
fit_linear_model <- linear_model(y  ~ ., lm_patho)
fit_linear_model$coefficients
```

## Perform linear regression with lm_grad_descent() function with colinearity problem
```{r}
fit_gd <- lm_grad_descent(y  ~ ., lm_patho)
fit_gd$coefficients
```

